Title here

### 2019-05-21 fertile.Rmd
broman, stodden, why R?

@@

@@

>>>>

# Karl Broman's Suggestions

* Encapsulate everything within one directory
* Separate raw data from derived data
* Separate data from code
* Use relative paths
* Choose filenames correctly
* Write README files

http://kbroman.org/steps2rr/pages/organize.html

@@

# Why focus on R?

* R is the most popular language for statistical programming and is specifically designed for statistics
* R is great for reprodubility because the code is readable by users, and RMarkdown is a great way to show/explain processes
* R is easy to install and begin using

--> from https://openresearchsoftware.metajnl.com/articles/10.5334/jors.bu/print/

@@

# Msc sources to look at:

### Victoria Stodden's "Implementing Reproducible Research" book
https://books.google.com/books?hl=en&lr=&id=JcmSAwAAQBAJ&oi=fnd&pg=PP1&dq=Victoria+stodden+reproducibility&ots=ym_gvSxMNH&sig=B5N6FlkoocVjIprIZevtvrL33qQ#v=onepage&q=coombes&f=false
